### 2018-07-04 README.Rmd
update the README CRAN Badge

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/naniar)](https://cran.r-project.org/package=naniar)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)

>>>>

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)
